---
title: "Analysis"
output: rmdformats::readthedown
---

# Setup
```{r setup}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(data.table)
library(plm) 
library(stringr)
library(stargazer)
```

# Kaggle data analyses

## Data preparation
```{r prepare data}
# Import data
dat_kaggle <- readRDS("data/dat_kaggle.rds") 

# Change column names
names(dat_kaggle)[4] <- "Topic_1"
names(dat_kaggle)[5] <-"Topic_2"
names(dat_kaggle)[6] <-"Topic_3"
names(dat_kaggle)[7] <-"Topic_4"
names(dat_kaggle)[8] <-"Topic_5"
names(dat_kaggle)[9] <-"Topic_6"
names(dat_kaggle)[10] <-"Topic_7"
names(dat_kaggle)[11] <-"Topic_8"
names(dat_kaggle)[12] <-"Topic_9"
names(dat_kaggle)[13] <-"Topic_10"
```


First, we will perform Least Squares Dummy Variables (LSDV) estimation with lm() to get an individual estimate for each unit. Second, we will run our model with plm(), which will do the same mechanics, yet it will not render each of the units intercept.

## Topics Model 
``` {r topic model , warning = FALSE}
topics_only_model <- lm(rating ~ Topic_1 + Topic_2 + Topic_3 + 
                      Topic_4 + Topic_5+  Topic_6 + Topic_7 + 
                      Topic_8 + Topic_9 + Topic_10, data = dat_kaggle)
summary(topics_only_model)
stargazer(topics_only_model,type = "text", out = "Table 1", 
          title = "Topic Model: Which Topics have better ratings?", 
          omit.stat=c("LL","ser","f","adj.rsq"), #omit character vector
          dep.var.labels.include = FALSE,
          column.labels = c("Rating"))
```

## Country Model 
``` {r country model, warning = FALSE}
# Transform country to categorical variable
dat_kaggle$country=as.factor(dat_kaggle$country)

# Create country dummy variables
# USA
dat_kaggle$USA <- NA 
dat_kaggle$USA[dat_kaggle$country=="USA"]<-1
dat_kaggle$USA[is.na(dat_kaggle$USA)]<- 0
# India
dat_kaggle$India <- NA
dat_kaggle$India[dat_kaggle$country=="India"]<-1
dat_kaggle$India[is.na(dat_kaggle$India)]<- 0
# UK
dat_kaggle$UK <- NA
dat_kaggle$UK[dat_kaggle$country=="UK"]<-1
dat_kaggle$UK[is.na(dat_kaggle$UK)]<- 0
# Canada
dat_kaggle$Canada <- NA
dat_kaggle$Canada[dat_kaggle$country=="Canada"]<-1
dat_kaggle$Canada[is.na(dat_kaggle$Canada)]<- 0
# France
dat_kaggle$France <- NA
dat_kaggle$France[dat_kaggle$country=="France"]<-1
dat_kaggle$France[is.na(dat_kaggle$France)]<- 0

# Country Model
country_model <- lm(rating ~ USA + India + UK + Canada + 
                France, data = dat_kaggle)
summary(country_model)
stargazer(country_model,type = "text", out = "Table 2", 
          title = "Country Model: USA, India, UK, Canada and France", 
          omit.stat=c("LL","ser","f","adj.rsq"), 
          dep.var.labels.include = FALSE,
          column.labels = c("Rating"))

```

## Duration Model 
```{r duration model, warning = FALSE}
# Duration Model
duration_model <- lm(rating ~ duration, data = dat_kaggle)
summary(duration_model)
stargazer(duration_model,type = "text", out = "Table 3", 
          title = "Duration Model", 
          omit.stat=c("LL","ser","f","adj.rsq"),
          dep.var.labels.include = FALSE,
          column.labels = c("Rating"))
# Note: longer films have higher ratings
```


## Horror Model
```{r horror model, warning = FALSE}
# Create country dummy variables
# South Korea
dat_kaggle$SK <- NA
dat_kaggle$SK[dat_kaggle$country=="South Korea"]<-1
dat_kaggle$SK[is.na(dat_kaggle$SK)]<- 0
# Sweden
dat_kaggle$Sweden <- NA
dat_kaggle$Sweden[dat_kaggle$country=="Sweden"]<-1
dat_kaggle$Sweden[is.na(dat_kaggle$Sweden)]<- 0
# Japan
dat_kaggle$Japan <- NA
dat_kaggle$Japan[dat_kaggle$country=="Japan"]<-1
dat_kaggle$Japan[is.na(dat_kaggle$Japan)]<- 0


# Horror Model
sk_horror_model <- lm(rating ~ SK*Topic_6, data = dat_kaggle)
summary(sk_horror_model)

sweden_horror_model <- lm(rating ~ Sweden*Topic_6, data = dat_kaggle)
summary(sweden_horror_model)

japan_horror_model <- lm(rating ~ Japan*Topic_6, data = dat_kaggle)
summary(japan_horror_model)

stargazer(sk_horror_model,sweden_horror_model,japan_horror_model,
          type = "text", out = "Table 4", 
          title = "Who Makes Better Horror Movies? South Korea vs.Sweden", 
          omit.stat=c("LL","ser","f","adj.rsq"),
          dep.var.labels.include = FALSE,
          column.labels = c("Rating in SK", "Rating in Sweden",
                            "Rating in Japan"))
#Note: Japanese movies add higher positive contributions to the rating. That is not the case for Japanese horror movies though, the effect of the interaction is statistically insignificant, negative and substantially small.
```

## Romance Model
``` {r romance model, warning = FALSE}
# Romance Model
france_romance_model <- lm(rating ~ France*Topic_7, data = dat_kaggle)
summary(france_romance_model)
uk_romance_model <- lm(rating ~ UK*Topic_7, data = dat_kaggle)
summary(uk_romance_model)

stargazer(france_romance_model,uk_romance_model,
          type = "text", out = "Table 5", 
          title = "Who Makes Better Romance Movies? France vs.UK", 
          omit.stat=c("LL","ser","f","adj.rsq"), 
          dep.var.labels.include = FALSE,
          column.labels = c("Rating in France", "Rating in UK"))
# Note: French romances have a statistically significant, negative effect on the rating. On th other hand, rating increases if a British movie turns out to be a romance. 
```

## Crime Model 
```{r crime model, warning = FALSE}
# Create country dummy variable 
#Denmark
dat_kaggle$Denmark <- NA 
dat_kaggle$Denmark[dat_kaggle$country=="Denmark"]<-1
dat_kaggle$Denmark[is.na(dat_kaggle$Denmark)]<- 0

# Crime Model
denmark_crime_model <- lm(rating ~ Denmark*Topic_9, data = dat_kaggle)
sweden_crime_model <- lm(rating ~ Sweden*Topic_9, data = dat_kaggle)
stargazer(denmark_crime_model ,sweden_crime_model,
          type = "text", out = "Table 6", 
          title = "Who Makes Better Police Movies? Denmark vs.Sweden", 
          omit.stat=c("LL","ser","f","adj.rsq"),
          dep.var.labels.include = FALSE,
          column.labels = c("Rating in Denmark", "Rating in Sweden"))
# Note: Denmark crime movies fare better than Swedish crime movies.
```

## USA Model
```{r USA mode, warning = FALSE}
# USA model
usa_crime_model <- lm(rating ~ USA*Topic_9, data = dat_kaggle)
usa_battle_model<- lm(rating ~ USA*Topic_1, data = dat_kaggle)
summary(usa_crime_model)
summary(usa_battle_model)
stargazer(usa_crime_model,usa_battle_model,
          type = "text", out = "Table 7", 
          title = "USA: Crime & Battle Movies", 
          omit.stat=c("LL","ser","f","adj.rsq"), 
          dep.var.labels.include = FALSE,
          column.labels = c("Rating of Crime Movies", "Rating of Battle Movies"))
# Note: USA-made killer-cop-gang-serial films seem to do  better than the average USA-made film.
```

## Indian Duration Model
```{r Indian duration model, warning = FALSE }
# India duration interaction effect model
india_len_model <- lm(rating ~ India*duration, data = dat_kaggle)
summary(india_len_model)
stargazer(india_len_model,
          type = "text", out = "Table 8", 
          title = "India: Are Longer Movies better than other Movies?", 
          omit.stat=c("LL","ser","f","adj.rsq"),
          dep.var.labels.include = FALSE,
          column.labels = c("Rating"))
# Note: We have derived above that Indian films tend to have higher ratings and that longer films have higher ratings, but when films are from India, a longer film is accompanied by a lower rating.
```

## Fixed Effect Model
```{r fe, warning = FALSE}
# Fixed effect model 
unit_fe_kaggle <- lm(rating ~ as.factor(country) + Topic_1 + Topic_2 + Topic_3 + 
                    Topic_4 + Topic_5 + Topic_6 + Topic_7 + Topic_8 + 
                    Topic_9 + Topic_10, data = dat_kaggle)
stargazer(unit_fe_kaggle,
          type = "text", out = "Table 9", 
          title = "Effect of Topic accounting for country", 
          omit.stat=c("LL","ser","f","adj.rsq"),
          dep.var.labels.include = FALSE,
          column.labels = c("Rating"))
# Note: Constant is quite moderate at 6.9, and the effects of each topic are all below 1 rating unit.
```
# Scraped data analyses 

## Data preparation 

``` {r prepare scraped data }
# Import scraped data 
dat_2020 <- readRDS("data/dat_2020.rds")

# Change column names
names(dat_2020)[9] <- "Topic_1"
names(dat_2020)[10] <-"Topic_2"
names(dat_2020)[11] <-"Topic_3"
names(dat_2020)[12] <-"Topic_4"
names(dat_2020)[13] <-"Topic_5"
names(dat_2020)[14] <-"Topic_6"
names(dat_2020)[15] <-"Topic_7"
names(dat_2020)[16] <-"Topic_8"
names(dat_2020)[17] <-"Topic_9"
names(dat_2020)[18] <-"Topic_10"

# Transform country to categorical variable
dat_2020$Country <- as.factor(dat_2020$Country)
```

## Topics Model (2020)
``` {r scraped topics model, warning = FALSE }
# Topics model using scraped data 
topics_scraped_model <- lm(Rating ~ Topic_1 + Topic_2 + Topic_3 + 
                      Topic_4 + Topic_5 +  Topic_6 + Topic_7 + 
                      Topic_8 + Topic_9 + Topic_10, data = dat_2020)
summary(topics_scraped_model)
stargazer(topics_scraped_model,type = "text", out = "Table 1", 
          title = "Topic Model: Which Topics have better ratings?", 
          omit.stat=c("LL","ser","f","adj.rsq"), 
          dep.var.labels.include = FALSE,
          column.labels = c("Rating"))
```

## Duration Model (2020)
```{r scraped duration model, warning = FALSE}
# Duration Model
duration_model_2020 <- lm(Rating ~ Duration, data = dat_2020)
summary(duration_model_2020)
stargazer(duration_model_2020,type = "text", out = "Table 11", 
          title = "Duration Model for 2020", 
          omit.stat=c("LL","ser","f","adj.rsq"),
          dep.var.labels.include = FALSE,
          column.labels = c("Rating"))
# Note: longer films have higher ratings
```

## British Model (2020)
```{r}
# UK
dat_2020$UK <- NA
dat_2020$UK[dat_2020$Country==" UK "]<-1
dat_2020$UK[is.na(dat_2020$UK)]<- 0

uk_romance_model_2020 <- lm(Rating ~ UK*Topic_7, data = dat_2020)
summary(uk_romance_model_2020)

# issue with stargazer
stargazer(uk_romance_model_2020,
          type = "text", out = "Table 12", 
          title = "British Romance Films for 2020", 
          omit.stat=c("LL","ser","f","adj.rsq"), 
          dep.var.labels.include = FALSE,
          column.labels = c("Rating in UK"))
```

## USA Model
```{r USA mode, warning = FALSE}

# USA
dat_2020$USA <- NA
dat_2020$USA[dat_2020$Country==" USA "]<-1
dat_2020$USA[is.na(dat_2020$USA)]<- 0

# USA model
usa_crime_model_2020 <- lm(Rating ~ USA*Topic_9, data = dat_2020)
usa_battle_model_2020 <- lm(Rating ~ USA*Topic_1, data = dat_2020)
summary(usa_crime_model_2020)
summary(usa_battle_model_2020)
stargazer(usa_crime_model_2020,usa_battle_model_2020,
          type = "text", out = "Table 13", 
          title = "USA: Crime & Battle Movies for 2020", 
          omit.stat=c("LL","ser","f","adj.rsq"), 
          dep.var.labels.include = FALSE,
          column.labels = c("Rating of Crime Movies", "Rating of Battle Movies"))
# Note: USA-made killer-cop-gang-serial films seem to do  better than the average USA-made film.
```


## Country Model 
``` {r scraped country model, warning = FALSE}
# Prepare country variable
dat_2020$Country <- as.character(dat_2020$Country)
dat_2020$Country <- str_trim(dat_2020$Country)

# Create country dummy variables
# USA
dat_2020$USA <- NA
dat_2020$USA[dat_2020$Country==" USA "]<-1
dat_2020$USA[is.na(dat_2020$USA)]<- 0

# Canada
dat_2020$Canada <- NA
dat_2020$Canada[dat_2020$Country==" Canada "]<-1
dat_2020$Canada[is.na(dat_2020$Canada)]<- 0

# Country Model
country_model_2020 <- lm(Rating ~ USA  + UK + Canada, data = dat_2020)
summary(country_model_2020)
stargazer(country_model_2020,type = "text", out = "Table 13", 
          title = "Country Model: USA, UK, Canada", 
          omit.stat=c("LL","ser","f","adj.rsq"), 
          dep.var.labels.include = FALSE,
          column.labels = c("Rating"))
# Note: Canadian and British movies seem to fare better than American movies.
```

## Fixed Effect Model
```{r scraped fe, warning = FALSE}
# Fixed effect model
unit_fe_2020 <- lm(Rating ~ Topic_1 + Topic_2 + 
                Topic_3 + Topic_4 + Topic_5+ Topic_6 + 
                Topic_7 + Topic_8 + Topic_9 + Topic_10 +
                as.factor(Country), data = dat_2020)
stargazer(unit_fe_2020,
          type = "text", out = "Table 14", 
          title = "Effect of each Topic accounting for country 2020", 
          omit.stat=c("LL","ser","f","adj.rsq"),
          dep.var.labels.include = FALSE,
          column.labels = c("Rating"))
# Note: Overall rating is high at 8.7, but the other estimates are statistically insignificant. 
```
## Scraped Metascore Model 
```{r scraped metascore model, warning = FALSE}
# Metascore model using scraped data 
metascore_model <- lm(Rating ~ Metascore + Topic_1 + Topic_2 + 
                Topic_3 + Topic_4 + Topic_5+ Topic_6 + 
                Topic_7 + Topic_8 + Topic_9 + Topic_10, 
                data = dat_2020)
stargazer(metascore_model,
          type = "text", out = "Table 15", 
          title = "Overall Effect of Rating with each Topic accounting for country 2020 and Metascore", 
          omit.stat=c("LL","ser","f","adj.rsq"),
          dep.var.labels.include = FALSE,
          column.labels = c("Rating"))
# Note: The Metascore seems to have a very marginal effect on Rating. The other estimates are statistically insignificant.
```