---
title: "imdb_kaggle"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(quanteda)
library(ggplot2)
library(ggrepel)
library(quanteda.textmodels)
theme_set(theme_minimal())

require(quanteda)
require(quanteda.corpora)
library(seededlda) ######## NOTE: You might need to install this
```

## Kaggle Data

```{r}
dat<-read.csv("imdb_1972-2019.csv")

# Exploring the dataset
names(dat)

# Selecting the variables we are going to use
dat1 <- dat %>% 
  select(Title, Year, Rating, Metascore, Description, Genre, Runtime..Minutes., Revenue..Millions.) %>% 
  distinct(Title, .keep_all = TRUE)
names(dat1)

# If you want to look at the duplicates 
dat %>% filter(duplicated(.[["Title"]]))
dat1 %>% filter(duplicated(.[["Title"]])) # to test that filter worked

# convert factors to character columns
dat2 <- dat1 %>%
  mutate_if(is.factor, as.character)

sapply(dat2, class) # to see current classes

```

## Structural Topic Model


```{r}
# Turn into corpus, linguistic data 
corp1 <- corpus(dat2, 
       text_field = "Description",
       docid_field = "Title")

docvars(corp1, "Title") <- dat1$Title ## Add back Title

# Create a document-feature matrix to enable text analysis
corp_dfm <- dfm(corp1, remove_punct = TRUE, remove_numbers = TRUE,
                remove_symbol = TRUE, remove = stopwords("en")) %>%
  dfm_trim(min_termfreq = 0.8, termfreq_type = "quantile") 
# only keeps top 5% of words - play around with (no doc limit)

tmod_lda_10 <- textmodel_lda(corp_dfm, k = 10) # k is number of topics
#tmod_lda_15 <- textmodel_lda(corp_dfm, k = 15) 
#tmod_lda_20 <- textmodel_lda(corp_dfm, k = 20) 

terms(tmod_lda_10, 15) # show top 15 most frequent terms of each topic

# how do you search by film 
```

Note: I started taking notes on what each of the categories could represent. 
Unfortunately, it seems like the model will save a different value each time it runs new. 
So we will need to figure out the methodology of how we want to save it and then check the results

ideas for k = 10 model
# topic1: military/spy
# topic2: romance
# topic3: ????
# topic4: nyc life?
# topic5: hs/college (teens)
# topic6: secrets
# topic7: family
# topic8: intergalactic adventure/war
# topic9: crime
# topic10: ????


```{r}
head(topics(tmod_lda_10), 20) # most likely topics by film

# assign topic as a new document-level variable
corp_dfm$Topic <- topics(tmod_lda_10)

# cross-table of the topic frequency (to see breakdown)
table(corp_dfm$Topic)

# explore the results
docvars(corp_dfm)

# this gives all the films of a specific topic
corp_dfm$Title[corp_dfm$Topic == "topic5"]
```
